### 2019-11-30 Common/chapters/data_processing.tex
Julien and Johan: create basic structure and chapters

Medical data is often represented over 16 bits. However, exporting images to PNG require 8-bit images. To transpose a 16-bit image to an 8-bit one, the procedure described by \ref{alg:16_to_8_bits_conversion} was applied.

@@

\section{PROSTATEx: From DICOM to NumPy arrays}

@@

\section{Lung CT Challenge - From DICOM to NumPy arrays}

@@

\begin{algorithm}
    \caption{Lung CT Challenge preprocessing}
    \label{alg:LungCTChallenge_preprocessing}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{main}{$dataset\_folder, train\_CSV, test\_CSV, output\_folder$}
        		\State Create output directories: $"output\_folder/True", "output\_folder/False"$\\
        		\State $csv\_training \gets read\_CSV(train\_CSV)$ \Comment{CalibrationSet.csv}
        		\State $csv\_test \gets read\_CSV(test\_CSV)$ \Comment{TestSet.csv}
            \State $csv\_concatenated \gets concat(csv\_training, csv\_test)$\Comment{Both CSV files contain similar information about different patients.}\\
            \For{$row$ in $csv\_concatenated$}
            		\State $patient\_id \gets row["Scan Number"]$
            		\State $slice\_number \gets row["Nodule Center Image"]$ \Comment{Value in $[1,\infty]$}
            		\State $finding\_id \gets row["Nodule Number"]$
            		\State $clinical\_significance \gets row["Diagnosis"]$\\
            		\If{$clinical\_significance$ == $"malignant"$ or $"Primary\ lung\ cancer"$}
            			\State{$clinical\_significance \gets True$}
            		\ElsIf{$clinical\_significance$ == $"benign"$ or $"Benign\ nodule"$}
            			\State{$clinical\_significance \gets False$}
            		\ElsIf {$"clinical\_significance$ == $"Suspicious\ malignant\ nodule"$}
            			\State{Continue}
            		\EndIf\\
                \For{$visit\ in\ patient\_id$'s folder}
                		\For{$mri\_type$ in $visit$}
                			\For{$dicom\_file$ in $mri\_type$}
                				\If {$slice\_number == dicom\_file.InstanceNumber$}
                					\State{$slice \gets normalize\_dicom(dicom\_file)$} \Comment{see section \ref{sec:data_manipulation}}
                					\State{Save $slice$ in $"output\_folder/clinical\_significance"$}
                				\EndIf
                			\EndFor
            			\EndFor
            		\EndFor
            \EndFor
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\section{NumPy arrays to PNG files}
Exporting to NumPy arrays instead of image files directly has multiple advantages. First of all, converting medical files to NumPy arrays or PNG files takes more time than converting NumPy arrays to image files. Reason for that is that the former requires a lot of operation as well as pixel normalization, whereas the latter is a mere conversion of one format to the other. This makes data more reusable. Then, it facilitates the debugging process by separating the conversion from medical files to PNG files into two different steps. Finally, the same processing script can be used to convert NumPy arrays from any dataset to PNG images, which eases operations such as generating different training-validation splits, augmenting data, etc.

>>>>

Medical data is often represented over 16 bits. However, exporting images to PNG require 8-bit images. To transpose a 16-bit image to an 8-bit one, the procedure described by algorithm \ref{alg:16_to_8_bits_conversion} was applied.

@@

\section{Processing flow}

Schema Datasets -> xxx\_preprocessing.py -> create\_dataset.py -> Train/Val

\subsection{PROSTATEx: From DICOM to NumPy arrays}

@@

\subsection{Lung CT Challenge - From DICOM to NumPy arrays}

@@

\begin{algorithm}
    \caption{Lung CT Challenge preprocessing}
    \label{alg:LungCTChallenge_preprocessing}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{main}{$dataset\_folder, train\_CSV, test\_CSV, output\_folder$}
        		\State Create output directories: $"output\_folder/True", "output\_folder/False"$\\
        		\State $csv\_training \gets read\_CSV(train\_CSV)$ \Comment{CalibrationSet.csv}
        		\State $csv\_test \gets read\_CSV(test\_CSV)$ \Comment{TestSet.csv}
            \State $csv\_concatenated \gets concat(csv\_training, csv\_test)$\Comment{Both CSV files contain similar information about different patients.}\\
            \For{$row$ in $csv\_concatenated$}
            		\State $patient\_id \gets row["Scan\ Number"]$
            		\State $slice\_number \gets row["Nodule\ Center\ Image"]$ \Comment{Value in $[1,\infty]$}
            		\State $finding\_id \gets row["Nodule\ Number"]$
            		\State $clinical\_significance \gets row["Diagnosis"]$\\
            		\If{$clinical\_significance$ == $"malignant"$ or $"Primary\ lung\ cancer"$}
            			\State{$clinical\_significance \gets True$}
            		\ElsIf{$clinical\_significance$ == $"benign"$ or $"Benign\ nodule"$}
            			\State{$clinical\_significance \gets False$}
            		\ElsIf {$"clinical\_significance$ == $"Suspicious\ malignant\ nodule"$}
            			\State{Continue}
            		\EndIf\\
                \For{$visit\ in\ patient\_id$'s folder}
                		\For{$mri\_type$ in $visit$}
                			\For{$dicom\_file$ in $mri\_type$}
                				\If {$slice\_number == dicom\_file.InstanceNumber$}
                					\State{$slice \gets normalize\_dicom(dicom\_file)$} \Comment{see section \ref{sec:data_manipulation}}
                					\State{Save $slice$ in $"output\_folder/clinical\_significance"$}
                				\EndIf
                			\EndFor
            			\EndFor
            		\EndFor
            \EndFor
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\subsection{NumPy arrays to PNG files}
Exporting to NumPy arrays instead of image files directly has multiple advantages. First of all, converting medical files to NumPy arrays or PNG files takes more time than converting NumPy arrays to image files. Reason for that is that the former requires a lot of operation as well as pixel normalization, whereas the latter is a mere conversion of one format to the other. This makes data more reusable. Then, it facilitates the debugging process by separating the conversion from medical files to PNG files into two different steps. Finally, the same processing script can be used to convert NumPy arrays from any dataset to PNG images, which eases operations such as generating different training-validation splits, augmenting data, etc.
